Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
Tried to fix alpha on the morton figure Changed the pipeline figure to fit the curvature framework
minor edit

In \cite{DGCI2013}, authors have defined the 2D digital curvature estimator
$\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ with
$\MCard(Y)$ the number of digital points of $Y$ and $Y \subset \Z^d$ the
intersection between the digital shape $\DigShape$ and a ball of digital radius
$R/h$ (we denote such quantity $\AreaC(Y,h)$ in dimension 2):
%
\begin{Definition}
  %
  Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
  (or $\R^3$ for the 3D mean curvature estimator), {\em digital curvature
  estimators} are defined for any point $\vx \in \R^2$ (or $\R^3$) as:
  %
  \begin{align}
    \forall 0 < h < R,\quad
    &\CurvH{R}(Z,\vx,h) \EqDef \frac{3\pi}{2R}
    - \frac{3\AreaC(\Ball{R/h}{\vx/h} \cap
    {Z}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
    &\MeanCurvH{R}(Z,\vx,h) \EqDef \frac{8}{3R}
    - \frac{4\VolC(\Ball{R/h}{\vx/h} \cap
    Z, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
  \end{align}
  %
  where $\Ball{R/h}{\vx/h}$ is the ball of digital radius $R/h$ centered on
  digital point $(\vx/h) \in Z$.
  %
  % \AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
  % \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
  % \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
  % the number of digital points in the intersection between $\Body{\DSh}{h}$ and
  % the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
  % $h^d$.\todo[inline]{J: Hum... pas top...}
  %
  % Similarly, $\hat{\lambda}_1$
  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
  % matrix of the digital points in the intersection between $Z$ and the ball.
  %
\end{Definition}
%
They have proved that estimating the 2D curvature and 3D mean curvature on digital
objets with volumetric integral information have the multigrid convergence
property \cite{DGCI2013}. For short, when the digital objet becomes finer and
finer, \ie when the digitization step $h$ tends to zero, the estimated quantity
on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
associated one on $\Bd{\Shape}$.
%
%Since our digital estimators are defined on
%digital shapes, in order to compare results with the exact curvature on
%Euclidean shape, we need to match points on boundary of the digital
%shape and points on the border of the Euclidean one.
%
Setting $R = kh^\frac{1}{3}$ on convex shapes
with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
related to the maximal curvature of the shape, they have:
%
\begin{align}
\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
\end{align}

@@

\begin{figure}[!htbp]
  \begin{center}
    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
  \end{center}
\caption{Morton codes associated to cells of a linear quatree. Each
   morton code of a child cell is obtained by adding a suffix to its
  parent code \emph{(left)}. The adaptive representation consists of
  quadtree cells whose depth is view point dependent
  \emph{(middle)}. Finally, adaptive Marching Cubes is used to
  generate the triangulation \emph{(right)}.}
\label{fig_quadtree_partitionning}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{figs/pipeline}
  \caption{ Summary our GPU pipeline. Data buffers are
    represented in green and computations in red. Each computation
    retrieves data from a buffer and fills a new one. }
  \label{fig_pipeline}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\framebox{octa $l_4$}}
   \subfigure[]{\framebox{octa $l_3$}}
   \subfigure[]{\framebox{octa $l_2$}}
   \subfigure[]{\framebox{octa $l_1$}}
   \subfigure[]{\framebox{octa $l_0$}}
  \end{center}
  \caption{fig multiresolution, courbure moyenne par ex}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

  \end{center}
  \caption{fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.}
  \label{fig:full}
\end{figure}

>>>>

In \cite{DGCI2013}, authors have defined the 2D digital curvature estimator
$\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ with
$\MCard(Y)$ the number of digital points of the intersection between a ball
$\Ball{R/h}{\vx/h}$ of digital radius $R/h$ and $\DigShape$ (we denote such
quantity $\AreaC(Y,h)$ in dimension 2):
%
\begin{Definition}
  %
  Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
  (or $\R^3$ for the 3D mean curvature estimator), {\em digital curvature
  estimators} are defined for any point $\vx \in \R^2$ (or $\R^3$) as:
  %
  \begin{align}
    \forall 0 < h < R,\quad
    &\CurvH{R}(Z,\vx,h) \EqDef \frac{3\pi}{2R}
    - \frac{3\AreaC(\Ball{R/h}{\vx/h} \cap
    {Z}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
    &\MeanCurvH{R}(Z,\vx,h) \EqDef \frac{8}{3R}
    - \frac{4\VolC(\Ball{R/h}{\vx/h} \cap
    Z, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
  \end{align}
  %
  where $\Ball{R/h}{\vx/h}$ is the ball of digital radius $R/h$ centered on
  digital point $(\vx/h) \in Z$.
  %
  % \AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
  % \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
  % \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
  % the number of digital points in the intersection between $\Body{\DSh}{h}$ and
  % the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
  % $h^d$.\todo[inline]{J: Hum... pas top...}
  %
  % Similarly, $\hat{\lambda}_1$
  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
  % matrix of the digital points in the intersection between $Z$ and the ball.
  %
\end{Definition}
%
They have proved that estimating the 2D curvature and 3D mean curvature on digital
objets with volumetric integral information have the multigrid convergence
property \cite{DGCI2013}. For short, when the digital objet becomes finer and
finer, \ie when the digitization step $h$ tends to zero, the estimated quantity
on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
associated one on $\Bd{\Shape}$.
%
%Since our digital estimators are defined on
%digital shapes, in order to compare results with the exact curvature on
%Euclidean shape, we need to match points on boundary of the digital
%shape and points on the border of the Euclidean one.
%
Setting $R = kh^\frac{1}{3}$ on convex shapes
with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
related to the maximal curvature of the shape, they have:
%
\begin{align}
\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
\end{align}

@@

\begin{figure}[!htbp]
  \begin{center}
    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton2}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
  \end{center}
\caption{Morton codes associated to cells of a linear quatree. Each
   morton code of a child cell is obtained by adding a suffix to its
  parent code \emph{(left)}. The adaptive representation consists of
  quadtree cells whose depth is view point dependent
  \emph{(middle)}. Finally, adaptive Marching Cubes is used to
  generate the triangulation \emph{(right)}.}
\label{fig_quadtree_partitionning}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{figs/pipeline2}
  \caption{ Summary our GPU pipeline. Data buffers are
    represented in green and computations in red. Each computation
    retrieves data from a buffer and fills a new one. }
  \label{fig_pipeline}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \subfigure[]{\framebox{octa $l_4$}}
   \subfigure[]{\framebox{octa $l_3$}}
   \subfigure[]{\framebox{octa $l_2$}}
   \subfigure[]{\framebox{octa $l_1$}}
   \subfigure[]{\framebox{octa $l_0$}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower using mipmap approximation of different levels : $l_4$, $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    %
    For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:full}
\end{figure}
